Driver coverage

### 2024-02-23 scomatic/reports/driver_coverage.Rmd
parameterise scomatic nextflow script, add header keys for reading mappings.csv, introduce STEP1 entry

@@

              # plot exons
              p[[id_i]][[gene_i]][[paste0('exons', p_suffix)]] <<-
                plot_exons(
                  p_df = lvl,
                  p_title = paste0(i, p_suffix)
                )
            })
        })
    })

>>>>

# function: plot stacked exon coverage
plot_exons_stacked <- function(p_df, p_title) {
  p_df %>% 
    # get only exonic sequence
    dplyr::filter(feature == 'exon') %>%
    # fix exon ordering
    dplyr::mutate(
      exon = exon %>% gsub('exon', '', .) %>% as.numeric(),
      facets = ifelse(is.na(celltype), 'all', 'by celltype')) %>%
    ggplot(aes(x = pos, y = depth, group = celltype, fill = celltype)) +
    geom_col(position = 'stack') +
    theme_classic() +
    theme(axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          panel.spacing = unit(.05, 'lines'),
          panel.border = element_rect(fill = NA)) +
    labs(title = paste(p_title, '(exons)')) +
    facet_grid(facets ~ exon, space = 'free_x', scales = 'free_x') 
}

@@

              # plot exons
              p[[id_i]][[gene_i]][[paste0('exons', p_suffix)]] <<-
                plot_exons(
                  p_df = lvl,
                  p_title = paste0(i, p_suffix)
                )

              # plot exons stacked
              p[[id_i]][[gene_i]][[paste0('exons_stacked', p_suffix)]] <<-
                plot_exons_stacked(
                  p_df = lvl,
                  p_title = paste0(i, p_suffix)
                )
            })
        })
    })
